---
title: "p8105_hw5_ltc2121"
output: github_document
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Data import and manipulation 

```{r}
full_df = 
  tibble(
    files = list.files("data/prob1/"),
    path = str_c("data/prob1/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

Tidy data

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Plot of observations over time 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

Import raw data and exploration

```{r}
raw_washp = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(state = case_when(city == 'Tulsa' ~ 'OK', 
                           TRUE ~ state),
    city_state = str_c(city, state, sep = ", ")) 

hom_df = raw_washp %>% 
  group_by(city_state) %>% 
  summarise(total_hom = n(), 
            unsolved_hom = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))) 
hom_df %>% 
  knitr::kable()

##############sig fig issue in the inline code ##################

```

This dataframe contains `r nrow(raw_washp)` rows and `r ncol(raw_washp)` columns. Each row represents an individual criminal homicide. The data includes information from `r raw_washp %>% select(city_state) %>% distinct %>% count` cities across the United States. The reported dates of cases range from `r min(raw_washp$reported_date)` to `r max(raw_washp$reported_date)`. The other key variables include details on victim name, age, race and sex. Another important notice about the dataframe was that the city Tulsa had been incorrectly matched with the state AK and needed to be corrected to be matched to the state OK. 


Making a Baltimore dataframe & prop.test 
```{r}
balti_df = hom_df %>% 
  filter(city_state == "Baltimore, MD")

test_res = prop.test(
    x = balti_df %>% pull(unsolved_hom),
    n = balti_df %>% pull(total_hom),
    alternative = c("two.sided"),
    conf.level = 0.95, 
    correct = TRUE) %>% 
  broom::tidy() %>% 
  mutate(conf.low = round(conf.low, 4),
         conf.high = round(conf.high, 4),
    CI = str_c(conf.low, conf.high, sep = "-")) %>% 
  select(estimate, CI)

```

Making function to estimate the proportion of homicides that are unsolved

```{r}
hom_prop = function(df) {
  
 test_res = prop.test(
    x = df %>% pull(unsolved_hom),
    n = df %>% pull(total_hom),
    alternative = c("two.sided"),
    conf.level = 0.95, 
    correct = TRUE) %>% 
  broom::tidy() %>% 
  mutate(conf.low = round(conf.low, 4),
         conf.high = round(conf.high, 4),
    CI = str_c(conf.low, conf.high, sep = "-")) %>% 
  select(estimate, CI)

}

```

Mapping function across all cities 

```{r}
hom_df_nest = 
  hom_df %>% 
  nest(data = total_hom:unsolved_hom)

hom_df_unnest = hom_df_nest %>% 
  mutate(
    et_CI = map(data, hom_prop)) %>%  
   unnest(et_CI)
```

Estimate of proportion plot

```{r}
hom_df_unnest %>% 
  separate(CI, c("low", "high"), "-") %>% 
  mutate(low = as.numeric(low), 
         high = as.numeric(high),
    ci = high - low, 
    city_state = fct_reorder(city_state, estimate)) %>% 
ggplot() +
  geom_point(aes(x = city_state, y = estimate)) +
  geom_errorbar( aes(x = city_state, ymin = estimate - ci, ymax = estimate + ci)) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 6)) +
   labs(
    title = "Estimated Proportion of Unsolved Homicides",
    x = "US City",
    y = "Proportion")
```

## Problem 3

Making t.test function and testing function
```{r}

sim_ttest = function(mu) {
  
  x = rnorm(n = 30, mean = mu, sd = 5)

  test_results = t.test(x)
  
  test_results %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
  
}

sim_ttest(mu = 0)

```

Simulation 1: mu = 0 for 5000 iterations

```{r}
sim_res_df_1 = 
  expand_grid(
    true_mean = 0,
    iteration = 1:5000  
  ) %>% 
  mutate(
    estimate_df = map(true_mean, sim_ttest)
  ) 

```

Simulation 2: mu = {1,2,3,4,5,6} for 5000 iterations

```{r}
sim_res_df_2 = 
  expand_grid(
    true_mean = c(1, 2, 3, 4, 5, 6),
    iteration = 1:5000  
  ) %>% 
  mutate(
    estimate_df = map(true_mean, sim_ttest)
  ) 

```

